### 2023-10-09 my_paper/Hadah-Attitudes.tex
edit codes, and add migration regressions
Change analysis over 3 years periods I also added county and msa level iat regressions

@@

@@

>>>>

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Generation County}
\label{plot01-regression-gen}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{All Generations}
\centering
\includegraphics[width=.9\linewidth]{figure/county-skin-iat-regression-all-gens.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{First-Generation}
\centering
\includegraphics[width=.9\linewidth]{figure/county-skin-iat-regression-first-gen.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation}
\centering
\includegraphics[width=.9\linewidth]{figure/county-skin-iat-regression-second-gen.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{Third-Generation}
\centering
\includegraphics[width=.9\linewidth]{figure/county-skin-iat-regression-third-gen.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}). I include region $\times$ year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is state-level bias. Each panel is the results from the same regression but on different samples that are divided by generation. Standard errors are clustered on the state level. The samples include first-, second-, and third-generation Asian children ages 17 and below who live in intact families. First-generation Asian immigrants are children that were born in a Asian country. Native-born second-generation Asian immigrants are children with at least one parent born in a Asian country. Finally, native-born third-generation Asian immigrants are children with native-born parents and at least one grandparent born in a Asian country.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Asian Identity and Bias: By Generation MSA}
\label{plot01-regression-gen}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{All Generations}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-skin-iat-regression-all-gens.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{First-Generation}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-skin-iat-regression-first-gen.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-skin-iat-regression-second-gen.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{Third-Generation}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-skin-iat-regression-third-gen.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}). I include region $\times$ year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Asian identity and the independent variable is state-level bias. Each panel is the results from the same regression but on different samples that are divided by generation. Standard errors are clustered on the state level. The samples include first-, second-, and third-generation Asian children ages 17 and below who live in intact families. First-generation Asian immigrants are children that were born in a Asian country. Native-born second-generation Asian immigrants are children with at least one parent born in a Asian country. Finally, native-born third-generation Asian immigrants are children with native-born parents and at least one grandparent born in a Asian country.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Hispanic Identity and Bias: By Parental Types County}
\label{plot01-regression-byparent}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{figure/county-by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Hispanic Fathers-Hispanic Mothers}
\centering
\includegraphics[width=.9\linewidth]{figure/county-by-parents-regs-hh.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Hispanic Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{figure/county-by-parents-regs-hw.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Hispanic Mothers}
\centering
\includegraphics[width=.9\linewidth]{figure/county-by-parents-regs-wh.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}). I include region $\times$ year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Hispanic identity and the independent variable is state-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Hispanic children ages 17 and below who live in intact families. Native-born second-generation Hispanic immigrant children with at least one parent born in a Spanish-speaking country.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Relationship Between Self-Reported Hispanic Identity and Bias: By Parental Types MSA}
\label{plot01-regression-byparent}
%First graph
\begin{subfigure}{.48\textwidth}
\caption{Second-Generation (All Parental Types)}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-by-parents-regs-all.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\caption{Hispanic Fathers-Hispanic Mothers}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-by-parents-regs-hh.png}
\end{subfigure}
%Third Graph
\begin{subfigure}{.48\textwidth}
\caption{Hispanic Fathers-White Mothers}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-by-parents-regs-hw.png}
\end{subfigure}
%Fourth Graph
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Hispanic Mothers}
\centering
\includegraphics[width=.9\linewidth]{figure/msa-by-parents-regs-wh.png}
\end{subfigure}
\caption*{\footnotesize{I show four panels of estimating equation (\ref{eq:identity_reg_bias}). I include region $\times$ year fixed effects with controls for sex, quartic age, and parental education. The dependent variable is self-reported Hispanic identity and the independent variable is state-level bias. Each panel results from the same regression but on different samples divided by parental types. Standard errors are clustered on the state level. The samples include second-generation Hispanic children ages 17 and below who live in intact families. Native-born second-generation Hispanic immigrant children with at least one parent born in a Spanish-speaking country.}}
\end{figure}
\end{center}

@@

\input{tables/tab46-iat-migration-tab}

### 2023-10-09 output/tables/tab47-county-iat_regression_tab_byparent_type.tex
Change analysis over 3 years periods I also added county and msa level iat regressions

\caption{Relationship Between Bias and Self-Reported Asian identity Among Second-Generation Asian Immigrants: By Parental Type \label{regtab-byparent-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{Parents Type} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{\makecell[c]{Both Parents \\ from Spanish \\ Speaking Country \\ (HH)}} & \multicolumn{1}{c}{\makecell[c]{Father \\ from Spanish \\ Speaking Country \\ (HW)}} & \multicolumn{1}{c}{\makecell[c]{Mother  \\ from Spanish \\ Speaking Country \\ (WH)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $A^2_{ist}$} & \specialcell{(2) \\ $A^2_{ist}$} & \specialcell{(3) \\ $A^2_{ist}$} & \specialcell{(4) \\ $A^2_{ist}$}\\
\midrule
Bias & -0.45*** & -0.15** & -1.16*** & -0.77***\\
 & (0.09) & (0.07) & (0.23) & (0.20)\\
Female & 0.00 & 0.00 & -0.01 & 0.02\\
 & (0.00) & (0.00) & (0.01) & (0.01)\\
College Graduate: Mother & 0.01 & -0.01 & 0.06* & 0.01\\
 & (0.01) & (0.01) & (0.03) & (0.02)\\
College Graduate: Father & 0.01 & 0.01* & -0.03 & 0.01\\
 & (0.01) & (0.01) & (0.03) & (0.03)\\
\midrule
Observations & 167,709 & 103,697 & 19,982 & 44,030\\
Year $\times$ Region FE & X & X & X & X\\
Mean & 0.72 & 0.96 & 0.38 & 0.32\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      type of parents with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include second-generation Asian children ages 17 and below who live in intact families. 
                      Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country.}
\item[3] \footnotesize{Column (1) includes the results to regression (\ref{eq:identity_reg_bias}) on all second-generation immigrants, 
                                        column (2) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father and mother that were born in a Asian country (HH),
                                        column (3) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father that was born in a Asian country and a native-born mother (HW), and
                                        column (4) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a native-born father and a mother that was born in a Asian country (WH).}
\item[4] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Relationship Between Bias and Self-Reported Asian identity Among Second-Generation Asian Immigrants: By Parental Type \label{regtab-byparent-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{Parents Type} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{\makecell[c]{Both Parents \\ from Spanish \\ Speaking Country \\ (HH)}} & \multicolumn{1}{c}{\makecell[c]{Father \\ from Spanish \\ Speaking Country \\ (HW)}} & \multicolumn{1}{c}{\makecell[c]{Mother  \\ from Spanish \\ Speaking Country \\ (WH)}} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
  & \specialcell{(1) \\ $A^2_{ist}$} & \specialcell{(2) \\ $A^2_{ist}$} & \specialcell{(3) \\ $A^2_{ist}$} & \specialcell{(4) \\ $A^2_{ist}$}\\
\midrule
Bias & 0.06 & 0.05 & 0.05 & 0.18\\
 & (0.14) & (0.13) & (0.68) & (0.33)\\
Female & 0.00 & 0.00 & 0.00 & 0.02\\
 & (0.00) & (0.00) & (0.01) & (0.01)\\
College Graduate: Mother & 0.01 & -0.01 & 0.06** & 0.01\\
 & (0.01) & (0.01) & (0.03) & (0.02)\\
College Graduate: Father & 0.00 & 0.01* & -0.03 & 0.01\\
 & (0.01) & (0.01) & (0.03) & (0.03)\\
\midrule
Observations & 167,733 & 103,709 & 19,982 & 44,042\\
State FE & X & X & X & X\\
Year FE & X & X & X & X\\
Mean & 0.72 & 0.96 & 0.38 & 0.32\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      type of parents with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include second-generation Asian children ages 17 and below who live in intact families. 
                      Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country.}
\item[3] \footnotesize{Column (1) includes the results to regression (\ref{eq:identity_reg_bias}) on all second-generation immigrants, 
                                        column (2) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father and mother that were born in a Asian country (HH),
                                        column (3) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a father that was born in a Asian country and a native-born mother (HW), and
                                        column (4) includes the results to regression (\ref{eq:identity_reg_bias}) on second-generation immigrants that who has a native-born father and a mother that was born in a Asian country (WH).}
\item[4] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}
